---
title: "hw5_prob3"
output: github_document
---
```{r, message = FALSE}
library(tidyverse)
```

## Problem 3

```{r}
homicide_raw = read_csv("data_hw5/homicide-data.csv")
summary(homicide_raw)
```

Comments on the raw data:  
The raw data contains 12 columns and 52,179 entries. Column variables are uid, reported_data, victim_last (all caped), victim_first (all caped), victim_race, victim_age, victim_sex, city, state, lat, lon, and disposition.  


Create a `city_state` variable.

```{r}
homicide_df = 
  homicide_raw |>
  mutate(
    city_state = paste(city, state, sep = ", ")
  )

```

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is "Closed without arrest" or "Open/No arrest").
```{r}
homicide_summary  = 
  homicide_df |> 
  group_by(city_state) |> 
  summarise(
    total = n(),
    unsolved = sum(disposition %in% c("Closed without arrest","Open/No arrest"))
  )
```

For the city of Baltimore, MD, use the `prop.test` function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe. 

```{r}
baltimore_summary = 
  homicide_df |> 
  filter(city_state == "Baltimore, MD") |> 
  summarise(
    total = n(),
    unsolved = sum(disposition %in% c("Closed without arrest","Open/No arrest"))
  )
```
```{r}
baltimore_prop = 
  prop.test(
    x = baltimore_summary$unsolved,
    n = baltimore_summary$total
  )
baltimore_prop_tidy  = 
  broom::tidy(baltimore_prop) |> 
  select(estimate, conf.low, conf.high)
baltimore_prop_tidy
```












